Determinants of Soccer Players' Market Values - Spain

### 2024-12-03 other/datasheet/france_datasheet.qmd
Added Datasheets

---
title: "Determinants of Soccer Players' Market Values - England"
author: John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
format: pdf
number-sections: true
---

@@

1. **For what purpose was the dataset created?**  
   To analyze determinants of soccer players’ market values, focusing on the Premier League. The goal is to enable robust insights for scouting, player valuation, and transfer market analysis.

@@

1. **What do the instances that comprise the dataset represent?**  
   Each instance represents a Premier League player and their associated attributes, including market value, performance metrics, and contextual variables.

2. **How many instances are there in total?**  
   The dataset contains 463 player records.

3. **Is the dataset a sample or does it contain all possible instances?**  
   The dataset is a comprehensive sample of Premier League players for the 2023/24 season.

@@

3. **What was the sampling strategy?**  
   Players were sampled based on their inclusion in the Premier League for the 2023/24 season.

@@

5. **Over what timeframe was the data collected?**  
   Data was collected during and after the 2023/24 Premier League season.

>>>>

---
title: "Determinants of Soccer Players' Market Values - France"
author: John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
format: pdf
number-sections: true
---

@@

1. **For what purpose was the dataset created?**  
   To analyze determinants of soccer players’ market values, focusing on the Ligue 1. The goal is to enable robust insights for scouting, player valuation, and transfer market analysis.

@@

1. **What do the instances that comprise the dataset represent?**  
   Each instance represents a Ligue 1 player and their associated attributes, including market value, performance metrics, and contextual variables.

2. **How many instances are there in total?**  
   The dataset contains 382 player records.

3. **Is the dataset a sample or does it contain all possible instances?**  
   The dataset is a comprehensive sample of Ligue 1 players for the 2023/24 season.

@@

3. **What was the sampling strategy?**  
   Players were sampled based on their inclusion in the Ligue 1 for the 2023/24 season.

@@

5. **Over what timeframe was the data collected?**  
   Data was collected during and after the 2023/24 Ligue 1 season.

### 2024-12-03 other/datasheet/germany_datasheet.qmd
Added Datasheets

---
title: "Determinants of Soccer Players' Market Values - France"
author: John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
format: pdf
number-sections: true
---

@@

1. **For what purpose was the dataset created?**  
   To analyze determinants of soccer players’ market values, focusing on the Ligue 1. The goal is to enable robust insights for scouting, player valuation, and transfer market analysis.

@@

1. **What do the instances that comprise the dataset represent?**  
   Each instance represents a Ligue 1 player and their associated attributes, including market value, performance metrics, and contextual variables.

2. **How many instances are there in total?**  
   The dataset contains 382 player records.

3. **Is the dataset a sample or does it contain all possible instances?**  
   The dataset is a comprehensive sample of Ligue 1 players for the 2023/24 season.

@@

3. **What was the sampling strategy?**  
   Players were sampled based on their inclusion in the Ligue 1 for the 2023/24 season.

@@

5. **Over what timeframe was the data collected?**  
   Data was collected during and after the 2023/24 Ligue 1 season.

>>>>

---
title: "Determinants of Soccer Players' Market Values - Germany"
author: John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
format: pdf
number-sections: true
---

@@

1. **For what purpose was the dataset created?**  
   To analyze determinants of soccer players’ market values, focusing on the Bundesliga. The goal is to enable robust insights for scouting, player valuation, and transfer market analysis.

@@

1. **What do the instances that comprise the dataset represent?**  
   Each instance represents a Bundesliga player and their associated attributes, including market value, performance metrics, and contextual variables.

2. **How many instances are there in total?**  
   The dataset contains 385 player records.

3. **Is the dataset a sample or does it contain all possible instances?**  
   The dataset is a comprehensive sample of Bundesliga players for the 2023/24 season.

@@

3. **What was the sampling strategy?**  
   Players were sampled based on their inclusion in the Bundesliga for the 2023/24 season.

@@

5. **Over what timeframe was the data collected?**  
   Data was collected during and after the 2023/24 Bundesliga season.

### 2024-12-03 other/datasheet/italy_datasheet.qmd
Added Datasheets

---
title: "Determinants of Soccer Players' Market Values - Germany"
author: John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
format: pdf
number-sections: true
---

@@

1. **For what purpose was the dataset created?**  
   To analyze determinants of soccer players’ market values, focusing on the Bundesliga. The goal is to enable robust insights for scouting, player valuation, and transfer market analysis.

@@

1. **What do the instances that comprise the dataset represent?**  
   Each instance represents a Bundesliga player and their associated attributes, including market value, performance metrics, and contextual variables.

2. **How many instances are there in total?**  
   The dataset contains 385 player records.

3. **Is the dataset a sample or does it contain all possible instances?**  
   The dataset is a comprehensive sample of Bundesliga players for the 2023/24 season.

@@

3. **What was the sampling strategy?**  
   Players were sampled based on their inclusion in the Bundesliga for the 2023/24 season.

@@

5. **Over what timeframe was the data collected?**  
   Data was collected during and after the 2023/24 Bundesliga season.

>>>>

---
title: "Determinants of Soccer Players' Market Values - Italy"
author: John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
format: pdf
number-sections: true
---

@@

1. **For what purpose was the dataset created?**  
   To analyze determinants of soccer players’ market values, focusing on the Serie A. The goal is to enable robust insights for scouting, player valuation, and transfer market analysis.

@@

1. **What do the instances that comprise the dataset represent?**  
   Each instance represents a Serie A player and their associated attributes, including market value, performance metrics, and contextual variables.

2. **How many instances are there in total?**  
   The dataset contains 441 player records.

3. **Is the dataset a sample or does it contain all possible instances?**  
   The dataset is a comprehensive sample of Serie A players for the 2023/24 season.

@@

3. **What was the sampling strategy?**  
   Players were sampled based on their inclusion in the Serie A for the 2023/24 season.

@@

5. **Over what timeframe was the data collected?**  
   Data was collected during and after the 2023/24 Serie A season.

### 2024-12-03 other/datasheet/spain_datasheet.qmd
Added Datasheets

---
title: "Determinants of Soccer Players' Market Values - Italy"
author: John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
format: pdf
number-sections: true
---

@@

1. **For what purpose was the dataset created?**  
   To analyze determinants of soccer players’ market values, focusing on the Serie A. The goal is to enable robust insights for scouting, player valuation, and transfer market analysis.

@@

1. **What do the instances that comprise the dataset represent?**  
   Each instance represents a Serie A player and their associated attributes, including market value, performance metrics, and contextual variables.

2. **How many instances are there in total?**  
   The dataset contains 441 player records.

3. **Is the dataset a sample or does it contain all possible instances?**  
   The dataset is a comprehensive sample of Serie A players for the 2023/24 season.

@@

3. **What was the sampling strategy?**  
   Players were sampled based on their inclusion in the Serie A for the 2023/24 season.

@@

5. **Over what timeframe was the data collected?**  
   Data was collected during and after the 2023/24 Serie A season.

>>>>

---
title: "Determinants of Soccer Players' Market Values - Spain"
author: John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
format: pdf
number-sections: true
---

@@

1. **For what purpose was the dataset created?**  
   To analyze determinants of soccer players’ market values, focusing on the La Liga. The goal is to enable robust insights for scouting, player valuation, and transfer market analysis.

@@

1. **What do the instances that comprise the dataset represent?**  
   Each instance represents a La Liga player and their associated attributes, including market value, performance metrics, and contextual variables.

2. **How many instances are there in total?**  
   The dataset contains 402 player records.

3. **Is the dataset a sample or does it contain all possible instances?**  
   The dataset is a comprehensive sample of La Liga players for the 2023/24 season.

@@

3. **What was the sampling strategy?**  
   Players were sampled based on their inclusion in the La Liga for the 2023/24 season.

@@

5. **Over what timeframe was the data collected?**  
   Data was collected during and after the 2023/24 La Liga season.
